---
title: "How Moving the Level 30 Gate Would Affect Retention Rates"
author: "PhiPrime"
date: "2/20/2021"
output: 
  slidy_presentation:
    keep_md: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = 'center')
```

```{r message = FALSE}
library(tidyverse)
```


## Control  
Currently a gate level is presented to the player when they reach level thirty. These levels give the player three ways of proceeding: replaying previous levels, inviting friends to download the app, or purchasing the keys to open the gate instantly.  
  

```{r fig.height= 5}
grid::grid.raster(png::readPNG("./Images/gate_level.png"))
```



## Alternative Placement  
Despite gate levels encouraging the player to invite more users or purchase content, they also can negatively impact player retention rates. To measure the magnitude of this possible negative impact we designed an A/B test. The control group encounter a gate level where it has been, level thirty, and the other half encounter one at level forty.


## Observations  
```{r echo = FALSE}
dat <- read.csv("./Data/cookie_cats.csv")
N <- dim(dat)[1]
dat <- dat %>% mutate(userid = as.character(userid),
                      version     = as.factor(version))

## Convert retention info into one var.

## Old code kept to explain formula's results
# dat <- mutate(dat, type = case_when(
#     !(retention_1 & retention_7) ~ 1,
#     !retention_1 & retention_7 ~ 2
#     retention_1 & !retention_7 ~ 3,
#     retention_1 & retention_7 ~ 4,# ))

dat <- mutate(dat, ret_type = as.factor(2*as.numeric(retention_1) +
                as.numeric(retention_7) + 1))

#count(dat, ret_type)
dat$ret_type <- as.factor(dat$ret_type)
levels(dat$ret_type) <- c("Full Retention", "Light Retention", 
                          "Quit Under a Week", "Quit Within a Day")
## While we're at it...
levels(dat$version) <- c("gate level at 30", "gate level at 40")
```

```{r eval = FALSE}
##Check for outliers    
sorted <- arrange(dat, sum_gamerounds)
list(No_attempt = sum(sorted$sum_gamerounds==0),
     One_try = sum(sorted$sum_gamerounds==1))
tail(sorted, 10) #One clear outlier

anom <- tail(sorted, 5)$sum_gamerounds
#sum_gamerounds is the number of rounds played 
#within the first 14 days after install
#this would mean that max value played on average...
anom/13/#Because ret...1 is FALSE so they didn't play at least that day
  24
#160 rounds per hour! with the next closest being 9.5/hr
#this seems like either data entry error or an observation
# invalidated by some external factor, such as using a program to
# play the game.
```

```{r}
#For ease of viewing the distribution, focus on the majority
cut <- 0.95
exp <- filter(dat, sum_gamerounds < quantile(sum_gamerounds, cut))
dis <- paste0("*", round((dim(exp)[1]/N)*100, 3), 
              "% of the data is represented.")
# paste0(dim(exp)[1], "/", N, ", ", dis)
```


We observed `r N` users that were randomly assigned either version of the game. One observation of the `r dat$version[which.max(dat$sum_gamerounds)]` was removed for being an outlier (over `r floor(max(dat$sum_gamerounds)/1000)` thousand rounds attempted within the 14 days). As a KPI of user retention rate, we checked for activity on the first and seventh day after install. Below are two graphs depicting the distribution of the number of rounds played for both versions; color is added to depict retention rates.


```{r fig.height = 4.3, fig.width = 7}
# Make a facet grid (version) histogram (rounds) with 
# four colored section to represent the possible
# retention rates. Include hline at gates

ggplot(exp, aes(sum_gamerounds)) +
  facet_grid(version~.) +
  geom_histogram(binwidth = 10, aes(fill = ret_type)) +
  labs(title = "Distribution of Rounds for each Testing Group",
       fill = "Retention",
       x = "Rounds Played",
       y = "Number of Users",
       caption = dis)
```



